---
title: "Geo-Genius: Unveil the Location"
author: "Andrea De Angelis"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

In this exercise, we'll use the `httr` and `jsonlite` packages in R to make an HTTP request to the OpenCage Geocoding API, which provides latitude and longitude coordinates for a given address. The exercise demonstrates how to make a GET request, parse the JSON response, and extract relevant information.

Objective: Determine the latitude and longitude of a given address using the OpenCage Geocoding API.

# Install and load the packages

Install and load the `httr` and `jsonlite` packages. 

```{r}

# install.packages("httr")
# install.packages("jsonlite")

library(httr)
library(jsonlite)

```

# Sign up for a free OpenCage API key

The link is available here: https://opencagedata.com/api 

```{r}
browseURL(url = "https://opencagedata.com/api")

api_key <- rstudioapi::askForPassword()
base_url <- "https://api.opencagedata.com/geocode/v1/json"
```

# Define an address

Create an `address` object with a character string address. 

```{r}

address <- "Gaiserstrasse 120, 9050 Appenzell Meistersruete"

```

# Make a GET request

Call the function `httr::GET()` with the `url` and `query` arguments. Tips: the query must be set as a list using `list()`. You will need to check the documentation to understand which parameters to give and how. Store the call response into `geocoding_response`. 

```{r}

geocoding_response <- httr::GET(base_url, 
                                query = list(key = api_key, q = address))

```

# Check the status code

```{r}

http_status(geocoding_response)

```

# Parse JSON and display

Good luck!

```{r}

resp <- httr::content(geocoding_response)
# jsonlite::fromJSON

# structure
str(resp, 1)

str(resp$results)

# acccess the results
resp$results[[1]]$geometry$lat
resp$results[[1]]$geometry$lan


```

